LSST Alerts: Science-Driven Options for Packets and their Distribution

### 2020-01-10 dmtn-tbd.tex
small ammendments

\subsection{EM Counterparts to GW Events}\label{ssec:latency_emgw}
{\it Some contents revised from a Slack conversation in the TVS chanel between Federica Bianco, Om Sharan Salafia, and Eric Bellm.}

@@

{\it Some contents based on text from and discussions with Tyler Pritchard (TVS member).}

>>>>

\subsection{EM Counterparts to GW Events}\label{ssec:latency_emgw}
{\it Some contents revised from a Slack conversation between Federica Bianco, Om Sharan Salafia, and Eric Bellm.}

@@

{\it Some contents based on text from and discussions with Tyler Pritchard.}
